%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\hypersetup {
  colorlinks=false,% hyperlinks will be black
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small\textbf{#1} & #2 \\
    \textit{\small#3} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
  \textbf{\Huge \scshape Fuad Ismail} \\ \vspace{1pt}
  \small \textit{} \\
  +62-838-9937-3595 $|$ \href{mailto:fuad1502@gmail.com}{fuad1502@gmail.com} $|$ 
  \href{https://github.com/fuad1502}{github.com/fuad1502}
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
\justifying
I am an ex-R\&D Hardware Engineer from Keysight Technologies Malaysia with over
4 years of experience in the hardware industry (RF, electronics, embedded).
Despite that, I am acquinted with software development, as my work frequently
require me to develop softwares, such as embedded software, mathematical
simulation, and computational libraries.

I took a career break since August 2023 due to personal reasons. I am currently
self studying Computer Science to break into the industry. See
\href{https://github.com/fuad1502/self-study-cs}{github.com/fuad1502/self-study-cs}
to know what I've achieved throughout my 7-months career break.

I am mainly interested in Systems Software (OS, Database, Distributed and
Embedded Systems) and my goal is to consistently contribute to the OSS
ecosystem by contributing to public repositories and building my own OSS
projects. Currently, I have contributed and will be contributing regularly to
\href{https://github.com/verilator/verilator}{Verilator}, an open-source
SystemVerilog simulator and lint system. 

I am a passionate learner commited to continuous learning and have a track
record of showing initiative at the workplace and deeply care about my work.

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Bandung Institute of Technology}{Bandung, Indonesia}
  {Electrical Engineering (BS), ABET Accredited, GPA
  3.81/4.0}{2014 - 2018}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
  \textbf{Programming Languages}{: Rust, Go, C, C++, Java, JavaScript,
  Python, SQL, SystemVerilog, MATLAB} \\
  \textbf{Developer Tools}{: Git, Docker/Podman, CMake, Make} \\
  \textbf{Libraries / Frameworks}{: React, Gin}
}}
\end{itemize}

%-----------PROJECTS-----------
\section{OSS Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
  {Bilbob: A Social Media for Your Pets}{February 2024 -- Present}
  {\href{https://github.com/fuad1502/bilbob}{github.com/fuad1502/bilbob}}
\begin{justify}
Bilbob is a Social Media platform written in Go with Gin web framework for the
  backend and Javascript with React for the frontend. This project originally
  meant as a learning exercise on end-to-end web development. Therefore, all
  functionality, such as registration and password storage management,
  authentication and session management, resource querying, are all written
  from scratch. Bilbob is live on
  \href{http://bilbob.fuadismail.com}{bilbob.fuadismail.com}.
\end{justify}

\resumeProjectHeading
  {Rubbler}{November 2023 -- Present}
  {\href{https://github.com/fuad1502/rubbler}{github.com/fuad1502/rubbler}}
\begin{justify}
  Rubbler is a RISC-V assembler written in Rust. This library was written with
  the main purpose of embedding a simple RISC-V assembler inside of a RISC-V
  CPU test bench code written with Verilator.
\end{justify}

\resumeProjectHeading
  {RVSV}{November 2023 -- Present}
  {\href{https://github.com/fuad1502/rvsv}{github.com/fuad1502/rvsv}}
\begin{justify}
  RVSV is a SystemVerilog implementation of a 5-stage pipelined RISC-V CPU.
  Verification code is written in C++ using Verilator and Rubbler.
\end{justify}

\resumeProjectHeading
  {KIBI}{October 2023 -- Present}
  {\href{https://github.com/fuad1502/kibi}{github.com/fuad1502/kibi}}
\begin{justify}
  KIBI is a simple typing test web application. Built with React and Spring
  Boot. KIBI is live on \href{http://kibi.fuadismail.com}{kibi.fuadismail.com}.
\end{justify}
\resumeSubHeadingListEnd

%-----------ADDITIONAL PROJECTS-----------
\section{Other Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
  {NAALG: Network Analyzer Algorithms C++ Library}{February 2024 -- Present}
  {Keysight Technologies}
\begin{justify}
  I initiated the development of NAALG due two things. First, I was tasked with
  developing a novel Time Domain Reflectometry (TDR) calculation from Vector
  Network Analyzer (VNA) measurements. Second, on a different project, I had
  just implemented a new calibration algorithm for an embedded VNA. Since both
  of this project involves calculation on VNA measurements, I realize that it
  would be nice to have a library that provides all of these VNA algorithms in
  one place. NAALG is similar to
  \href{https://scikit-rf.readthedocs.io}{scikit-rf}, but uses high performant
  implementation in C++ to enable usage in embedded real-time measurement
  applications.
\end{justify}
\resumeProjectHeading
  {Custom Telecommunication Device (GMSK + TDM Transceiver)}{February 2024 -- Present}
  {Hariff Daya Tunggal Engineering}
\begin{justify}
  My team was tasked with developing a fully custom telecommunication device.
  My role was in developing the physical (PHY) and medium access control (MAC)
  layer on an \textit{All Programmable SoC (APSoC)}. The PHY layer is written
  in Verilog, while the MAC layer is written in C. Communication between the
  two layers uses Direct Memory Access (DMA).
\end{justify}
\resumeProjectHeading
  {Automatic Identification System Search and Rescue Transponder}{February 2024 -- Present}
  {Labs247}
\begin{justify}
  Automatic Identification System (AIS) Search and Rescue Transponder (SART) is
  a radio device used to locate distressed vessels. My role was in developing
  all of the electronic and embedded software aspect of the device, and
  production. We use \href{https://freertos.org}{FreeRTOS} Real-Time Operating
  System to enable low power usage and multiple tasks management. Up till now
  the device is still in production.
\end{justify}
\resumeSubHeadingListEnd

%-----------RELEVANT EXPERIENCE-----------
\section{Relevant Experience}
\resumeSubHeadingListStart
\resumeSubheading
  {Software Engineer}{February 2021 - October 2021}
  {Lumina Industries}{Jakarta, Indonesia}
\resumeItemListStart
\resumeItem{Wrote the Windows middleware for a Virtual Camera software using
Win32 API.}
\resumeItem{Developed image processing features using C++ with OpenCV.}
\resumeItem{Worked remotely with a medium-sized team from various nationalities
(USA, Taiwan, and Indonesia).}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ADDITIONAL EXPERIENCE-----------
\section{Additional Experience}
\resumeSubHeadingListStart
\resumeSubheading
  {R\&D Hardware Engineer}{January 2022 -- August 2023}
  {Keysight Technologies}{Penang, Malaysia}
\resumeItemListStart
\resumeItem{Initiated the development of NAALG, a network analyzer algorithms
C++ library.}
\resumeItem{Demonstrated iniatiative by voluntarily improving an internal
software tool used by our team.}
\resumeItem{Demonstrated initiative by introducing a better software
development workflow.}
\resumeItem{Significantly improve the measurement accuracy of an embedded VNA
product by introducing and implementing a better calibration algorithm.}
\resumeItem{Successfully extend the measurement bandwidth of an embedded VNA
product.}
\resumeItem{Fixed a technical issue in an embedded VNA product and wrote a
technical paper on it.}
\resumeItem{Collaborate in a team from various time zones (USA, Europe, and
Malaysia).}
\resumeItemListEnd

\resumeSubheading
  {R\&D Radio Frequency Engineer}{August 2022 -- February 2021}
  {Hariff Daya Tunggal Engineering}{Bandung, Indonesia}
\resumeItemListStart
\resumeItem{Wrote MATLAB simulations to evaluate system-level design tradeoffs
for the development of a fully custom telecommunication device.}
\resumeItem{Implemented the PHY and MAC layer of a fully custom telecommunication
device on an APSoC using Verilog and C.}
\resumeItem{Designed a schematic for a fully custom telecommunication device.}
\resumeItemListEnd

\resumeSubheading
  {R\&D Electronic Design Engineer}{August 2018 -- August 2020}
  {Labs247}{Jakarta, Indonesia}
\resumeItemListStart
\resumeItem{Lead the development of telecommunication product (AIS SART) which
is still in production up till now.}
\resumeItem{Involved in the development of medical product (CPAP BiPAP
machine).}
\resumeItem{Demonstrated initiative by suggesting cost-saving solutions that
avoids vendor lock in and introduced an efficient production workflow.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
